Results

### 2021-10-11 Manuscript/Manuscript_Discussion_TD.Rmd
update

We propose a new integrated framework to help researcher collect and screen scientific publications characterized by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools. By sharing the tool as an open source R package and following a modular design of the tool, we tried to adopt some of the so called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making]. Our tool thus consists of three main components: 1) an integrated query-based citation search and management engine, 2) an active machine learning based citation screener, and 3) a data-driven query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well known scientific databases (i.e. Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases. The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the online databases limitations in terms of traffic and download quota.\

Most SRH tools we are aware of, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) that focus on a particular topic [@visser2010performing] or rely on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia]. To our knowledge, our tool is the first capable to fully automatize searching on three different well known scientific databases and to import raw data from five of them. Mixing different database is fundamental to have a more complete view of the literature on a topic [@bajpai2011search; @wilkins2005embase; @woods1998medline]: in our results, 18.7% of the positive matches were unique for one of the different data sources and no positive record was present among all of them (data not shown).\

We improved the transformation of textual data into actionable numeric inputs [@ananiadou2006text; @cohen2008getting] by using network analysis to identify associated terms, labelled as non-consecutive ngrams, conferring particular meaning when present together into a text while not necessary being close to each other. A similar network approach was used to merge redundant terms, in order to make model estimation more efficient and reduce possible noise. The use of network inspired modeling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word of consecutive ngram models.\

The framework's record screening module implements active machine learning based classification, bringing improvements at various levels. At the base of our classification algorithm we use BART [@chipman2010bart; @kapelner2013bartmachine], a Bayesian machine learning technique characterized by exceptional predictive performance and speed even in large dataset. This Bayesian approach explores distributions of decision trees which are justified by the data [@hastie2009boosting], while using a set of prior distributions to avoid overfitting by discouraging excessively deep trees, long sequences of trees, or extreme predicted probabilities.\

To further improve generalizability we ran multiple replications of the model and averaged their record predictive distributions; this technique, known as ensembling, has been shown to improve out-of-sample predictive performance []. In a Bayesian setting, this effect comes from a reduction of the probability mass in the tails of the predictive distributions while not shifting their locations (i.e., it decreases variance without impacting bias). Instead, imposing stronger general priors against extreme predictions would decreased variance but also shifted the distribution mass towards a non-decision zone, therefore increasing bias.\

Using more then one model replica greatly improved sensitivity and efficiency, with a performance stabilization after 10 replications (Suppl. Mat. S2); since the number of model replications greatly impacted computation times we decided to use ten replicas since it was also associated with the higher sensitivity in the same performance cluster. The variability between models derives only from the randomness in the MCMC fitting phase []; an alternative was to impose additional variability by bootstrapping [] but this approach decreased performance (Suppl. Mat. S2), probably due to the low proportion of positive matches in the data and the loss of information with bootstrapping in unbalanced classification tasks [].\

Given that our framework can (automatically) collect a vast amount of records, most records will be non-relevant (labelled negative). This strong imbalance between positive and negative records [@sampson2011precision] can affect sensitivity []. To overcome the problem, we oversampled the positive records ten times before model fitting. Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance. A known risk with oversampling of the target class is the missclassification of negative records as positive [], but since in our approach all predicted positive are manually reviewed we are ensured to achieve always 100% specificity/positive predictive value. An alternative approach would be record weighting to change error costs during estimation [] but the BART implementation we used did not allow observation weighting and using simple oversampling allows to use different modeling engines. Furthermore, the simple query ordering of the record during the record collection allowed for a far higher prevalence of relevant records in the initial training set (17.2%) compared to the overall one (0.11%) and this boosts the overall sensitivity of the model.\

At every iteration the researcher is asked to manually review a number or records, defined by the size of the uncertainty zone, which is dynamically shrinking (Suppl. Mat. S2 Fig. 1). This uncertainty zone is identified by joining the distribution of probabilities produced by exploiting the Bayesian nature of BART for both the positive and negative record groups. The researcher therefore doesn't need to choose a priori the number of records to review but just the size of the uncertainty zone (by setting the PPD quantiles used to built it) and after how many iterations with no new positive matches to stop. This is where our approach offers a major innovation in overcoming of simple stopping rules in SRA classification tasks []. Since our approach requires researchers to review both unlabelled records with a positive predicted label and those with a PPD inside the uncertainty zone, it can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

To evaluate performance we avoided the classic random out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study] because we deemed them not realistic in this setting. It is instead more relevant to estimate the long run sensitivity of our prediction method in finding all relevant records in the whole data set. Since the records are ordered, again a random approach would not work since it assumes that the prevalence of positive records is equal on average in every possible sample [@tashman2000out], while instead it drops as more records are considered (Fig. 2). We instead used a Bayesian model to estimate the likelihood of a positive match given the prediction scores of the BART model. This approach showed to fit the data very well (high $R^2$) and the Bayesian predictive distribution can be exploited to draw a worse case scenario given the data.\

Our framework achieved a very high sensitivity screening just 1.34% of all downloaded records, a sensible reduction in workload. The approach reached 98.8% sensitivity during the hyperparameter optimization (deterministic, small sample) and on the whole data set we predicted a theoretical sensitivity of 100% [93.5%, 100%] in the first session and of 97.3% [73.8%, 100%] in the second, a lower value as is expected by the probabilistic accumulation of random events. Both results are above the usual results in the field [@o2015using] and in line with the 92% average sensitivity estimated after human only screening [@edwards2002identification]. In one interesting case, the model spotted a misclassification during initial labeling, demonstrating its robustness and its value also as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards]. Finally, albeit the simple query based ordering did concentrate most of the relevant matches in the first 20-25 thousands records, some relevant records would have required almost the full data set to be manually checked to be found.\

The model takes ~5-20 minutes per iteration to perform predictions in session 1 (17755 documents) and 20-40 minutes in session 2 (98371 documents) on a 8 core, 2.5 GhZ, 16 GB RAM laptop from 2014 and that equate to 1-3 days per session to manually review and perform predictions, for a total of 1-2 weeks for the whole process, a huge saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating]. To our knowledge, our data sets are larger than what common in most SRA studies [@o2015using; @olorisade2016critical], emphasizing the reliability of the tool in real world scenarios.\

The last module of our framework is a data-driven query generation algorithm. The creation of an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximize the number of relevant search results while minimizing the total number of results. We propose a solution based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the posterior predicted probabilities; the technique tries to extract high sensitivity subqueries from the labeled data, enrich them with negative terms to increase specificity [@abdelmgeid2008using] and then let researcher evaluate them and pick the most meaningful ones. The framework will then join them and remove redundancies. The aim is to generate a second query that complement the first human made one and help find possible missing records not found during the first session.\

The generated query allowed to retrieve few more positive matches not found in session 1 at the cost of a large increase in the amount of documents. One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules internalized by the classification model, showing which combination of terms was particularly relevant and even spotting authors and locations associated to the topic of study. The generated query therefore acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to spot bias in black box classification algorithms [@malhi2020explainable] and that is increasingly legally required for high-stack machine learning applications [@bibal2021legal; @bibal2020impact].\

It is important to note that this process is entirely data-driven. The algorithm is only aware of the "world" defined by the data set, itself generated by a specific search query focused on a particular topic. Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results. The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare associated infections) of our research.\

As reported, our framework builds on modularity. We designed it in order to easily implement complete independency of the main modules in future iterations. In our view it would be possible to easily add custom citation search and parsing functions for other scientific databases, alternative text features building algorithms and alternative machine learning modules. We deem such interoperability extremely relevant, because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning, but each of its components could benefit greatly from the recent improvements in text mining. For example, our text feature generation approach is based on the boolean bag-of-words paradigm, and surely it could be improved by more nuanced text representations: it could be evaluated if feature transformations like Tf-Idf [@baeza1999modern; @ananiadou2006text], would be advantageous, even if we hypothesize that tree based classification algorithms like BART are robust enough to not need such operation. Word embedding could be considered, which transform terms in semantic vectors based on the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context; another option would be to use unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis, etc., [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\

Our classification algorithm can be implemented with any Bayesian supervised machine learning method which produces full PPDs; therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian]. Even more interesting would be to test  advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher level features in the text like term context and sequences, long distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\

>>>>

We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
By sharing the tool as an open-source R package and following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
Our tool thus consists of three main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) an active machine learning-based citation screener, and 4) a data-driven search query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e. Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\ 
The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the online database in terms of traffic and download quota.\

The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
A similar network approach was applied to merge redundant terms to make model estimation more efficient and reduce possible noise.
The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\

The framework's record screening module implements active machine learning-based classification [@settles2009active, @miwa2014reducing] based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine], adopting best practices from other SRA studies and bringing improvements at various levels.\
As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
However, its Bayesian foundation provides further benefits:
less sensitivity on hyperparameter choices, natural regularisation through priors, and, especially, predictive distributions as output in place of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
The algorithm runs multiple replications of the model and averages their predictive distributions to create an "ensemble", a technique that has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble] as confirmed by the hyperparameter evaluation (Suppl. Mat. S2).
This approach reduces the uncertainty in the predictive distribution tails due to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the centre and stabilising the distributions (i.e., decreasing variance without impacting bias).
On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which performance stabilises.\
We also evaluated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory, it was demonstrated to be slightly detrimental (Suppl. Mat. S2) compared to same-data ensembling [@diez2015diversity].\

A low rate of relevant matches (class imbalance) is typical in literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and such strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
To overcome the problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance.\
A known risk with positive oversampling is the misclassification of negative records [@ramezankhani2016impact].
However, since all predicted positives get manually reviewed in our approach, we are always ensured to achieve 100% specificity/positive predictive value: the only price for the increased sensitivity due to oversampling is a larger number of records to review.\
An alternative to oversampling would be applying different weights and/or cost to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
also, using simple oversampling permits broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
Finally, ordering the records by query term frequency (simple query ordering) generate a far higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), and this boosts the sensitivity of the model.\

One of the central innovations we introduced is the concept of "uncertainty zone", which derives from the Bayesian foundation of the classification model.
This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Suppl. Mat. S2 Fig. 1).
This approach permits overcoming the limitations of active learning related to selecting a stopping rule which focus on hard thresholds or propose singular new items at each iteration instead of a batch [@laws2008stopping; @miwa2014reducing; @zhu2010confidence]. Our algorithm instead requires more general parameters, like the PPD intervals based on which the uncertainty zone is built and the maximum number of iterations with no positive matches after which a session is concluded; also, the hyperparamer evaluation shows that the algorithm is robust against variations in these parameters.\
Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

We evaluated performance as the capability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while reviewing as few of them as possible (i.e., sensitivity $\times$ efficiency).
We avoided the classic out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
Such methods primarily assume that the probability of a positive match is equal on average in both the training and test set [@tashman2000out];
this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and the active learning algorithm, determining a lower positivity rate in the unlabelled records (Fig. 2).
Also, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
Instead, to estimate overall sensitivity, we implemented a surrogate, strongly regularised [@van2021bayesian], Bayesian regression model relying on just the lower interval of the generated PPD as predictor to abstract the active learning-based classification process and achieve a maximum entropy [@harremoes2001maximum] probabilistic estimate of the number of missed positive matches among the unreviewed records.
This simple surrogate model fitted the data very well ($R^2$ consistently above 97%), and its posterior predictive distribution could be exploited to explore worse case scenarios in terms of sensitivity.\

Our framework achieved very high sensitivity by screening a markedly small fraction of all records, bringing a sensible reduction in workload.\
Based on the surrogate model, we predicted a theoretical median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
efficiency increased significantly in the second session since only a few new positive matches were found, but given the large number of records, uncertainty regarding sensitivity also expectedly increased.\
Both results are above the usual performance in the field [@o2015using] and in line with the 92% average sensitivity estimated after human-only screening [@edwards2002identification].
In one interesting case, the model spotted a human misclassification in the initial training set, demonstrating its robustness and value as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
Finally, albeit the simple query ordering already concentrated most of the relevant matches in the first 20-25 thousand records, without the tool support some relevant records would have required almost the complete data set to be manually checked to be found.\

The model took ~5-20 minutes per iteration to perform predictions in session 1 (17,755 documents) and 20-40 minutes in session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM laptop from 2014;
including manual record review, one session required 1-3 days of work, for a total of 1-2 weeks for the whole process (including record collection).
That is a considerable saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
To our knowledge, our data sets are larger than what is typical in most SRA studies [@o2015using; @olorisade2016critical], emphasising the reliability of the tool in real-world scenarios.\

The last module of our framework is a data-driven query generation algorithm.
Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of results.
Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD with a human review step and an efficiency-driven query joiner.
The aim is to generate a second query that helps find records missed during the first session search.
The generated query allowed indeed to retrieve few more positive matches not found in session 1, but at the cost of a significant increase in the number of documents.\
One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
The generated query, therefore, acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to understand and spot bias in black-box classification algorithms [@malhi2020explainable];
explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
It is important to note that this process is entirely data-driven.
The algorithm is only aware of the "world" defined by the data set generated by a specific search query focused on a particular topic.
Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research to the query.\

As reported, our framework builds on modularity.
We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning.
However, each of its components could benefit considerably from the recent improvements in text mining.\
For example, our text processing approach is based on the boolean bag-of-words paradigm, and indeed it could be improved by more nuanced text representations.
It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operation.
Word embedding, a technique that transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis or Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\
Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\

The field of literature review automatisation is becoming mature and ripe with innovation, and we expect an increasing use of such technologies to confront the ever-faster production of scientific literature.
We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.
We tried to contribute to the field with an innovative methodology and tool that provides excellent performance and easy integration with existing systematic review pipelines.

### 2021-10-11 Manuscript/Manuscript_Introduction.Rmd
update

We apply this solution in the production of a systematic review evaluating the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms with a focus on antimicrobial-resistant strains. The systematic review protocol is published in [@newis].

>>>>

We apply this solution in the production of a systematic review evaluating the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms with a focus on antimicrobial-resistant strains. The systematic review protocol is published in [@newis].\
We give an overview of the framework in the Methods section and its results once applied to the topic of patient referral network modeling in Results section; in the Discussion we lay out the methodological justification behind the different components and features of the framework.

### 2021-10-11 Manuscript/Manuscript_Methods.Rmd
update

We built an R [@rstat] based framework with the goal of simplifying two aspects of systematic reviews: record acquisition and classification. The framework is composed of several components which act together while being independent enough to be in principle be substituted by alternative implementations, given that the structure of the intermediate data outputs is respected. See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
The tasks carried out by the framework are grouped into "sessions", that is, a set of actions that starts from using a search query to obtain a set of scientific publications (records), which will be eventually labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig. 1). From this labelled set, the framework allows to generate a new query and perform a new session.\
The researcher should use the framework with a specific query from which she expects a high relevant/non-relevant record ratio.\
Follows a description of the framework's components.\

@@

### Label prediction
We used a Bayesian Additive Regression Trees (BART) machine learning model [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record of being relevant, given the information coded into the enriched DTM. BART models have several advantages: as other boosted trees techniques [@hastie2009boosting], they can model complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power. However, the Bayesian framework they are built on provides further benefits: less sensitivity on hyperparameter choices, natural regularization, and, most of all, predictive distributions as output in place of point-wise predictions.\
We set up the BART model to use 2000 iterations (after 250 burn-in iterations) and 50 trees; we used a $k$ value of 2 to regularized extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction]. Since the goal is to find all positive matches (i.e., focus on sensitivity), positive records are oversampled ten times.\
The output is a posterior predictive distribution (PPD) of each record's probability of a positive match. An ensemble of ten models was fitted to improve prediction stability by averaging the predictions between models.\
To choose how to label a record, we exploit the uncertainty typical of Bayesian estimates to decide a record label and whether it requires manual evaluation, an approach joining the "uncertainty" and "certainty" selection criteria of previous work in the field [@miwa2014reducing]. To describe the process formally, we define

@@

### Performance evaluation
The citation data is not a random sample and it is ordered and for this reason, simple random sample based predictive performance approaches would not be useful (see Discussion). We focused on estimating the expected total sensitivity in the dataset, using a Bayesian logistic regression to model the label of the manually reviewed records on the lower bound of the [98% PrI] produced by our algorithm and then using this last model to produce a predictive cumulative distribution of the number of missed positive records. For this model, we used weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$). Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing a plausible worst-case scenario. The quality of the model was evaluated through Bayesian $R^2$ [@gelman2019r] of which we reported the posterior median and 90% Credible Interval [90% CrI].\
The predictive distribution of the number of missed positive records allows to estimate the expected long-run *Sensitivity* and the *Work saved over random* (WSoR) of the algorithm. The WSoR is based on a negative hypergeometric model to estimate the number of records to manually label to find the same number of positives if records were evaluated in random order [@chae1993presenting]; the WSoR is then one minus the ratio of the reviewed records over this number. For the number of predicted positive records, the sensitivity and WSoR, we reported the truncated 90% PrI [trunc. 90% PrI], which is the uncertainty interval bounded at the number of observed total positive records: since each positive match is manually verified, the probability of a number of total positive records lower than observed is zero.

>>>>

We built an R [@rstat] based framework with the goal of simplifying two aspects of systematic reviews: record acquisition and classification. The framework is composed of several modules which communicate through intermediate outputs stored in common formats (Comma Separated Values/or Microsoft Excel™), which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline. See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
The tasks carried out by the framework are grouped into "sessions", that is, a set of actions that starts from a search query to obtain a set of scientific publication data (records), which will be eventually labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig. 1). From this labelled set, the framework can generate a new query and perform a new session to find records possible missed by the first query.\
The researcher should use the framework with a starting query from which she expects a high relevant/non-relevant record ratio.\
Follows a description of the framework's components.\

@@

### Label prediction
We used a Bayesian Additive Regression Trees (BART) machine learning model [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record of being relevant, given the information coded into the enriched DTM.
We set up the BART model to use 2000 MCMC iterations (after 250 burn-in iterations) and 50 trees; we used a $k$ value of 2 to regularized extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction]. Since the goal is to find all positive matches (i.e., focus on sensitivity), positive records are oversampled ten times.\
The output is a posterior predictive distribution (PPD) of each record's probability of a positive match. An ensemble of ten models was fitted to improve prediction stability by averaging the predictions between models.\
To choose how to label a record, we exploit the uncertainty typical of Bayesian estimates to decide a record label and whether it requires manual evaluation, an approach joining the "uncertainty" and "certainty" selection criteria of previous work in the field [@miwa2014reducing]. To describe the process formally, we define

@@

### Performance evaluation
Each literature corpus is unique per database/search query, so we did noWe focused on estimating the expected total sensitivity in the dataset, using a surrogate [] Bayesian logistic regression to model the record labels on the lower bound of the [98% PrI] produced by our algorithm and then using this last model to produce a predictive cumulative distribution of the number of missed positive records. For this model, we used weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$). Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing a plausible worst-case scenario. The quality of the model was evaluated through Bayesian $R^2$ [@gelman2019r] of which we reported the posterior median and 90% Credible Interval [90% CrI].\
The predictive distribution of the number of missed positive records allows to estimate the expected long-run *Sensitivity* and the *Work saved over random* (WSoR) of the algorithm. The WSoR is based on a negative hypergeometric model to estimate the number of records to manually label to find the same number of positives if records were evaluated in random order [@chae1993presenting]; the WSoR is then one minus the ratio of the reviewed records over this number. For the number of predicted positive records, the sensitivity and WSoR, we reported the truncated 90% PrI [trunc. 90% PrI], which is the uncertainty interval bounded at the number of observed total positive records: since each positive match is manually verified, the probability of a number of total positive records lower than observed is zero.

### 2021-10-11 Manuscript/Manuscript_Results.Rmd
update

---
title: "Results"
date: "`r lubridate::today()`"
output:
  pdf_document:
    includes:
      in_header: header.tex
  github_document: default
---

@@

As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set). The best set of parameters suggested an initial input of 250 labelled records with 20x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval. On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated). A summary of the results of the grid search is reported in Table 3 in Suppl. Mat. S2.

>>>>

---
title: "Results"
date: "`r lubridate::today()`"
output:
  # pdf_document:
  #   includes:
  #     in_header: header.tex
  github_document: default
---

@@

As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set). The best set of parameters suggested an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval. On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated). A summary of the results of the grid search is reported in Table 3 in Suppl. Mat. S2.
